The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-13 analysis/paper/paper.qmd
Add abstract

---
title: "The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach"
author:
  - Claudiu Forgaci:
      correspondence: "yes"
      email: C.Forgaci@tudelft.nl
      orcid: 0000-0003-3218-5102
      institute: tud
institute:
  - tud:
      name: Delft University of Technology
      address: Julianalaan 134, 2628 BL, Delft, Zuid-Holland, The Netherlands
title-block-published: "Last updated"  
date: now
date-format: long
format: 
  # docx:
  #   reference-doc: "../templates/template.docx" # Insert path for the DOCX file
  pdf:
    template: "../templates/plos_latex_template.tex"
execute:
  echo: true
  warning: false
  message: false
  comment: "#>"
  fig-path: "../figures/"
  fig-dpi: 600
filters:
  - ../templates/scholarly-metadata.lua
  - ../templates/author-info-blocks.lua
  - ../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  urbanism; education; post-master; text mining
highlights: |
  These are the highlights. 
---

>>>>

---
title: "The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach"
author:
  - Claudiu Forgaci:
      correspondence: "yes"
      email: C.Forgaci@tudelft.nl
      orcid: 0000-0003-3218-5102
      institute: tud
institute:
  - tud:
      name: Delft University of Technology
      address: Julianalaan 134, 2628 BL, Delft, Zuid-Holland, The Netherlands
title-block-published: "Last updated"  
date: now
date-format: long
format: pdf
  # docx:
  #   reference-doc: "../templates/template.docx" # Insert path for the DOCX file
  # pdf:
  #   template: "../templates/plos_latex_template.tex"
execute:
  echo: true
  warning: false
  message: false
  comment: "#>"
  fig-path: "../figures/"
  fig-dpi: 600
filters:
  - ../templates/scholarly-metadata.lua
  - ../templates/author-info-blocks.lua
  - ../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Prompted by the closure of the European post-Master of Urbanism (EMU) at TU Delft,
  this paper aims to describe the legacy of the EMU. To that end, it reports on the
  analysis of the graduation theses produced over 2007-2021 when the program was running.
  The text mining approach allows for a close scrutiny of the latent thematic patterns, 
  and evolutions thereof, found in the full texts of the theses. Results reveal # topics
  that are to a large extent consistent with the set-up of the program in two thematic 
  semesters at TU Delft and three possible exchange semester locations, each characterised 
  by a specific approach. The paper discusses the relevance of the findings for the
  state of the profession and education in the field. Set up as a reproducible research
  compendium accompanied by a published FAIR dataset of the theses and an interactive
  dashboard, the analysis presented can be both reproduced and applied to other datasets. 
keywords: |
  urbanism; education; post-master; text mining; topic 
highlights: |
  These are the highlights. 
---
